---
title: "homework-number-5"
author: "Natalie Robinson"
date: "November 17, 2017"
output: html_document
---

# Homework 5

## Bootstrapping Standard Errors and CIs for Linear Models

** 1. Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept). **

```{r}
# to load the dataset
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = TRUE)
head(d)
```

```{r}
# to run a linear regression
m <- lm(data = d, log(HomeRange_km2) ~ log(Body_mass_female_mean))
m
```

```{r}
library(ggplot2)
g <- ggplot(data = d, aes(x= log(Body_mass_female_mean), y = log(HomeRange_km2)))
g <- g + geom_point()
g <- g + geom_smooth(method = "lm")
g
```

The slope is 1.036 and the intercept is -9.441


** 2. Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient. **

```{r}
set <- data.frame(NULL) # sets up a dummy variable to hold our 1000 simulations
n <- 213 # there are 213 entries in the Kalimar and Cooper dataset
for (i in 1:1000) { # simulate 1000 times
  sample <- d[sample(nrow(d), n, replace = TRUE), ]
  m <- lm(log(HomeRange_km2) ~ log(Body_mass_female_mean), data = sample) # fitting the same model each time
  coef <- m$coefficients # get the simulated intercepts and slopes
  set <- rbind(set, coef) # make a dataframe to hold the simulated intercepts and slopes
}
colnames(set) <- c("Intercept", "Slope")
head(set) 
# this generates a sampling distribution for each B coefficient
```

* Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.

```{r}
df <- data.frame(cbind(sd(set$Intercept), sd(set$Slope), quantile(set$Intercept, 0.025), quantile(set$Intercept, 0.975), quantile(set$Slope, 0.025), quantile(set$Slope, 0.975)))
colnames(df) <- c("SE_Intercept", "SE_Slope", "LowerCI_Intercept", "UpperCI_Intercept", "LowerCI_Slope", "UpperCI_Slope")
df
```

* How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?

```{r}
summary(m)$coef # to find the SE of the entire dataset
```
The SE from the entire dataset is shown above. The values are very similar to the bootstrapped SE.


* How does the latter compare to the 95% CI estimated from your entire dataset?

```{r}
confint(m, level = 0.95)
```

These values are the 95% CI from the entire dataset with 213 observations.
The CI values for the simulation with 1000 observations (above) are very similar.

## Extra Credit Part 1

** Write a FUNCTION that takes as its arguments a dataframe, “d”, a linear model, “m” (as a character string, e.g., “logHR~logBM”), a user-defined confidence interval level, “conf.level” (with default = 0.95), and a number of bootstrap replicates, “n” (with default = 1000). Your function should return a dataframe that includes: beta coefficient names; beta coefficients, standard errors, and upper and lower CI limits for the linear model based on your entire dataset; and mean beta coefficient estimates, SEs, and CI limits for those coefficients based on your bootstrap. **

d = dataframe
m = linear model
conf.level = user-define confidence interval level (default = 0.95)
n = number of bootstrap replicates (default = 1000)

```{r}
bootstrap <- function(d, m, conf.level = 0.95, n = 1000) {

  # beta coefficients and SE based on entire dataset 
  summary_m <- coef(summary(m))
  beta_coef_names <- c("beta0", "beta1")
  beta_coefs <- summary_m[ ,1]
  SE <- summary_m[ ,2]
  
  # CI based on entire dataset
  lowerCI <- confint(m, level = conf.level)[ ,1]
  upperCI <- confint(m, level = conf.level)[ ,2]
  
  # Bootstrapping (modified from part 2)
  set <- data.frame(NULL) # sets up a dummy variable to hold simulations
  for (i in 1:n) { # simulate n times
    sample <- d[sample(nrow(d), n, replace = TRUE), ]
    m <- lm(m, data = d) # fitting the same model each time
    coef <- m$coefficients # get the simulated intercepts and slopes
    set <- rbind(set, coef) # make a dataframe to hold the simulated intercepts and slopes
  }
  
  # Mean beta coefficients based on bootstrap
  intercepts <- as.numeric(c(set$Intercept))
  mean_intercept <- mean(intercepts)
  
  slopes <- as.numeric(c(set$Slopes))
  mean_slope <- mean(slopes)
  
  # SE and CI based on bootstrap (from part 2)
  df <- data.frame(cbind(sd(set$Intercept), sd(set$Slope), quantile(set$Intercept, 0.025), quantile(set$Intercept, 0.975), quantile(set$Slope, 0.025), quantile(set$Slope, 0.975)))
colnames(df) <- c("SE_Intercept", "SE_Slope", "LowerCI_Intercept", "UpperCI_Intercept", "LowerCI_Slope", "UpperCI_Slope")
  
  return <- data.frame(beta_coef_names, beta_coefs, SE, lowerCI, upperCI, mean_intercept, mean_slope, df)
  return
}
```

Plugging back in data from this homework to test the function:
```{r}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/KamilarAndCooperData.csv")

d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = TRUE)
m <- lm(data = d, log(HomeRange_km2) ~ log(Body_mass_female_mean))
conf.level <- 0.95
n <- 1000

bootstrap(d, m, conf.level = 0.95, n = 1000)
```
This is not working correctly. I'm not sure why the values from the boostrap are not showing up.

## Extra Credit Part 2

** Graph each beta value from the linear model and its corresponding mean value, lower CI and upper CI from a bootstrap as a function of number of bootstraps from 10 to 200 by 10s. HINT: the beta value from the linear model will be the same for all bootstraps and the mean beta value may not differ that much! **

```{r}
# beta coefficients based on entire dataset 
summary_m <- coef(summary(m))
beta_coefs <- summary_m[ ,1]

set <- data.frame(NULL)

for (i in seq(from = 10, to = 200, by = 10)) {
  # finish this
}

g <- ggplot(data = set, aes(x = beta_coefs, y = mean_value))
```
I need to work on this more